### 2020-06-25 magic_paper.tex
Added fragment figures

The Wigner distributions of different types of qutrit states are illustrated in~\cref{fig:wstate_examples}.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:maxmix}%
    \includegraphics[height=2cm]{figs/maxmixed.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:zero}%
    \includegraphics[height=2cm]{figs/zerostate.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:bound}%
    \includegraphics[height=2cm]{figs/boundstate.pdf}
    %\caption{Bound state}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:strange}%
    \includegraphics[height=2cm]{figs/strangestate.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$.
    \nick{Explain what a magic / bound magic state is in intro}
    }%
    \label{fig:wstate_examples}
\end{figure}

@@

A vector $\bmy$ \emph{$\bmd$--majorizes} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorization into a finite set of inequalities.
\begin{theorem}\label{thm:dmajor}
    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
\end{theorem}
A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.\nick{move around}
\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
    \nick{Recast in terms of magic - replace with~\cref{fig:test}?}
    }
    \label{fig:lctoy}
\end{figure}

@@

We first show that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ discussed in~\cref{sec:mono}
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	Borrowing notation from~\cref{def:lc}, let $k_\star$ be the index of the smallest non-negative component $\tilde{\bmz}_{\pi(i)}$ of $\tilde{\bmz}^\downarrow$.
	It is clear by the construction of the Lorenz curve described in~\cref{def:lc} that the maximum is achieved at
	\begin{equation}
		x_{k_\star} \coloneqq \sum_{i=1}^{k_\star} (\W{\sigma})_{\pi(i)},
	\end{equation}
	and takes the value
	Note that all components of $\W{\sigma}$ are positive, so $(\bmu^\downarrow)_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.

	Suppose all components of $\W{\rho}$ are non-negative.
	Then, $\sn{\rho}=0$ and the global maximum of the Lorenz curve is dictated by the normalisation of $\W{\rho}$ so we trivially have
	\begin{equation}
		\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 = 1 + \sn{\rho}.
	\end{equation}

	Suppose that $\W{\rho}$ has at least one negative component.
	Let $k$ be the index of the smallest non-negative component of $\bmu^\downarrow$.
	Then the maximum of the Lorenz curve $\lc{\rho}{\sigma}$ occurs at $x_k$, just before its slope becomes negative. 
	The $x$-coordinate $x_k$ is different for different $\sigma$--fragments but the value of the maximum is the same and is given by
	\begin{align}
		&\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}
		= \lc{\rho}{\sigma}(x_k)
		= \sum\limits_{i=1}^k (\W{\rho})_{\pi(i)} \\
		&= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
		= 1 + \sn{\rho}.
	\end{align}

\end{proof}
\nick{Perhaps create Lorenz curve appendix and put the proof there as well as how functional form and discretised form of Lorenz curves relate}
\ddd{[This I think is a simpler approach:]}
The Lorenz curve of $L_{\bmx |\bmd}(x)$ is defined by piecewise linear sections sequentially linking the points $\{ (a_k,b_k)\}$ where $a_k = \sum_{i=1}^k x_i$, $ b_k = \sum_{i=1}^k d_i$ and we order the components such that $\tilde{x}_i:=x_i / d_i$ form a non-increasing sequence in $i$.

Now let $k_\star$ be the index of the smallest non-negative number in $(\tilde{x}_i)$, and define 
\begin{align}
a_\star &:= \sum_{i=1}^{k_\star} x_i\\
b_\star &:= \sum_{i=1}^{k_\star} d_i.
\end{align}
It is then clear that $L_{\rho|\sigma}(x)$ attains a maximum value of $a_\star \ge 1$ at the point $x = d_\star$.

Note that since $\bmd \ge \mathbf{0}$, for $i > k_\star$ we have that $x_i \le 0$, independent of the particular $\bmd$ we use. Therefore the value of $a_\star$ is independent of the particular fragment, with only the location of the maximum ($x=b_\star$) varying from fragment to fragment. \ddd{[This method is tidier.]}

@@

As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, and for the $k$-copy state we have that
\begin{equation}\label{eq:Skmax}
    \max_x{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^k \right),
\end{equation}
independent of the particular $\sigma$--fragment. \ddd{[We should also give for what value of $x$ this maximum occurs.]} 
%1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
%\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n} = \frac{1}{2} \left [  (1+a)^k - (1-a)^k \right ]

\subsection{Distilling out magic in a fragment}
\nick{why this new subsection?}
Consider, as an example, the problem of purifying out magic from a noisy state of the form
\begin{equation}
    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
\end{equation}
in $\O_\sigma$.
At noise levels $\epsilon \geq \frac{3}{4}$, the state is sufficiently noisy so as the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ no longer contains negativities. 
At any $\epsilon \leq \frac{3}{4}$, we can investigate the distillation process resulting in a single-copy state with sufficiently low target $\epsilon_{\tau}$,
\begin{equation}\label{eq:sdist}
	\rho_{\rm{S}}(\epsilon)^{\otimes k} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
\end{equation}

@@

\nick{Condition in~\cref{eq:ethresh} is informally written. Can also define 
\begin{equation}\label{eq:ethresh}
	k_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{k:\ k \in \mathbb{N}, \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
\end{equation}}
We now examine the MSD process~(\ref{eq:sdist}) in greater detail for some important $\sigma$--fragments.

@@

If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
Dephasing channels and general bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}

\nick{Replace the following with discussion of MSD process in the unital fragment for various numbers of copies $k$ vs mana}

In~\cref{fig:distill}, we examine the purifying process 
\begin{equation}\label{eq:purify}
    \rho_{\rm{S}}^{\otimes k}(\epsilon_{\rm{th}}) \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(0.05),\ \sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id
\end{equation}
with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$--fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/ratios.pdf}
    \caption{\textbf{Noise threshold ratios.} Mana and Lorenz curve ratios for the Strange state purifying process in~\cref{eq:purify}.
    The ratios are calculated for different numbers of initial state copies and different $\sigma$--fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
    \nick{Consider set of pure stabilizer states instead of $(1-p)\ketbra{0} + p \frac{1}{3}\id$ perhaps}
    }
    \label{fig:distill}
\end{figure}

@@

Consider a system driven by Hamiltonian $H$ and a circuit consisting of thermal operations.
The computational basis now coincides with the energy eigenbasis of Hamiltonian $H$.
We denote the thermal state $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.\nick{expand}

Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}
The Wigner distribution of thermal state $\gamma_\beta$ always consists of strictly positive components,
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
so pre-order $\prec_{\gamma_\beta}$ is well defined.

We generalise the analysis of~\cref{sec:unital} \nick{expand}.
\nick{Include figure with noise threshold level $\epsilon_{\rm{th}}$ in $y$-axis and temperature $\beta$ in $x$-axis. for various numbers of copies $k$.}

@@

We can also view $\sigma$--fragments as an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
However, states which are incomparable in $\R$ remain incomparable and conversions between states which are comparable in $\R$ may no longer be possible.
\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$. 
Moreover, these obey
	\begin{enumerate}
        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
    \end{enumerate}
We call $\R'$ a \emph{contravariant fragment} of $\R$.
\end{definition}
Note that a contravariant projection is always a surjective mapping for both states and operations, so that the conditions in~\cref{def:contraproj} make sense.
The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms. 
Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.

>>>>

The Wigner distributions of different types of qutrit states are illustrated in~\cref{fig:wstate_examples}.
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:maxmix}%
    \includegraphics[height=2cm]{figs/maxmixed.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:zero}%
    \includegraphics[height=2cm]{figs/zerostate.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:bound}%
    \includegraphics[height=2cm]{figs/boundstate.pdf}
    %\caption{Bound state}%
    }\hspace{8pt}%
    \subfigure[][]{%
    \label{fig:strange}%
    \includegraphics[height=2cm]{figs/strangestate.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Qutrit Wigner distributions of varying magic.} 
    \subref{fig:maxmix} Maximally mixed state $\frac{1}{3}\id$; \subref{fig:zero} Stabilizer zero state $\ketbra{0}{0}$; \subref{fig:bound} A non-stabilizer Wigner-positive state; \subref{fig:strange} Magic strange state $\ket{{\rm{S}}} = \frac{1}{\sqrt{2}}(\ket{1} - \ket{2})$ \nick{CITE}.
    \nick{Explain what a magic / bound magic state is in intro}
    }%
    \label{fig:wstate_examples}
\end{figure}

@@

A vector $\bmy$ \emph{$\bmd$--majorizes} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorization into a finite set of inequalities.
\begin{theorem}\label{thm:dmajor}
    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
\end{theorem}
A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
    \nick{Recast in terms of magic - replace with~\cref{fig:test}?}
    }
    \label{fig:lctoy}
\end{figure}

@@

We first show that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ discussed in~\cref{sec:mono}
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	For notational simplicity, denote $(\W{\rho})_i = \W[\bmx]{\rho},\ i = 1,\dots, d^2$ and similarly for $\W{\sigma}$.
	We choose the index mapping so that the vector of component ratios, 
	\begin{equation}
		\tilde{\bm{w}} \coloneqq \left(\frac{(\W{\rho})_1}{(\W{\sigma})_1}, \dots, \frac{(\W{\rho})_{d^2}}{(\W{\sigma})_{d^2}} \right)^T,
	\end{equation}
	is sorted in the sense that $\tilde{\bm{w}} = \tilde{\bm{w}}^\downarrow$.
	Note that all components of $\W{\sigma}$ are positive, so $(\tilde{\bm{w}})_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.

	Let $k_\star$ be the index of the smallest non-negative component of $\tilde{\bm{w}}^\downarrow$.
	Then, $(\W{\rho})_i < 0$ if and only if $i > k_\star$, so the maximum of Lorenz curve $\lc{\rho}{\sigma}(x)$ takes the value 
	\begin{equation}
		\lc{\rho}{\sigma}(x_{k_\star}) = \sum_{i=1}^{k_\star} (\W{\rho})_i,
	\end{equation}
	and is achieved at
	\begin{equation}\label{eq:maxloc}
		x_{k_\star} \coloneqq \sum_{i=1}^{k_\star} (\W{\sigma})_i.
	\end{equation}

	The location of the maximum ($x=x_{k_\star}$) varies from fragment to fragment, but its value is independent of $\sigma$,
	\begin{equation}
		\lc{\rho}{\sigma}(x_{k_\star})
		= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
		= 1 + \sn{\rho}.
	\end{equation}

@@

As an example, consider the qutrit Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
It is the simplest non-trivial case to analyse because the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, and for the $k$-copy state we have that
\begin{equation}\label{eq:Skmax}
    \max_x{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = \frac{1}{2}\left (1 + \left(\frac{5}{3}\right)^k \right),
\end{equation}
independent of the particular $\sigma$--fragment. \ddd{[We should also give for what value of $x$ this maximum occurs.]} \nick{It will have the form of~\cref{eq:maxloc} and probably cannot be simplified more other than finding $k_\star$ exactly.}
%1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}
%\sum_{n=1, n \mbox{ odd}}^k a^n \binom{k}{n} = \frac{1}{2} \left [  (1+a)^k - (1-a)^k \right ]

Consider the problem of purifying out magic from a noisy Strange state,
\begin{equation}
    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
\end{equation}
in $\O_\sigma$.
At noise levels $\epsilon \geq \frac{3}{4}$, the state is sufficiently noisy so as the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ no longer contains negativities. 
At any $\epsilon \leq \frac{3}{4}$, we can investigate the distillation process resulting in a single-copy state with sufficiently low target $\epsilon_{\tau}$,
\begin{equation}\label{eq:sdist}
	\rho_{\rm{S}}(\epsilon)^{\otimes k} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
\end{equation}

@@

\nick{Condition in~\cref{eq:ethresh} is informally written. Can also define 
\begin{equation}\label{eq:ethresh}
	k_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{k:\ k \in \mathbb{N}, \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
\end{equation}}
We now examine the MSD process~(\ref{eq:sdist}) in specific $\sigma$--fragments.

@@

If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
Dephasing and bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}

In~\cref{fig:unital_distill}, we examine the purifying process of~\cref{eq:sdist} with $\epsilon_\tau = 0.05$ which describes all circuits that respect the unital symmetry.
Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
\nick{Explain asymptotic behaviour?}
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/unital_distill.pdf}
    \caption{\textbf{Noise thresholds in unital fragment.} Mana and Lorenz curve noise thresholds for the Strange state purification process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities.
    }
    \label{fig:unital_distill}
\end{figure}

@@

Consider a system driven by Hamiltonian $H$ and a circuit consisting of thermal operations.
The computational basis now coincides with the Hamiltonian eigenbasis.
We denote the thermal state at temperature $\beta^{-1}$ by $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.\nick{expand}

Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}.
The Wigner distribution of any thermal state $\gamma_\beta$ always consists of strictly positive components,
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
so pre-order $\prec_{\gamma_\beta}$ is well defined.

We generalise the analysis of unital fragments into any circuit with thermalisation noise parametrised by the temperature $\beta^{-1}$.
In~\cref{fig:thermal_distill}, we examine the majorization bound for the same purification process of~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
The curves plotted suggest that there exists a fragment $\O_{\gamma_{\beta_{\rm{max}}}}$ which allows for a highest noise threshold at any given number of copies of the initial state.
Adding more copies results in a lower optimal temperature $\beta^{-1}$.

\begin{figure}[t]
    \centering
    \includegraphics[scale=0.5]{figs/thermal_distill.pdf}
    \caption{\textbf{Noise thresholds in thermal fragments.} Lorenz curve ratios for the Strange state purifying process in~\cref{eq:sdist} with $\epsilon_\tau = 0.05$.
    The peaks of each curve indicate the optimal temperature $\beta_{\rm{max}}$ that allows for the highest noise threshold at every given number of initial state copies $k$.
    The line $\epsilon = \frac{3}{4}$ indicates the threshold noise beyond which the Strange state no longer contains negativities.
    }
    \label{fig:thermal_distill}
\end{figure}

@@

We can also view $\sigma$--fragments as an example of reducing the structure of a magic theory $\R$ to a subtheory with a tractable pre-order.
However, states which are incomparable in $\R$ remain incomparable and conversions between states which are comparable in $\R$ may no longer be possible.
\begin{definition}[\textbf{Contravariant projection}]\label{def:contraproj}
	Let $\R = (\F, \O)$ be a resource theory with pre-order $\prec_\R$. 
Then a \emph{contravariant resource projection} of $\R$ onto a resource theory $\R'$ with pre-order $\prec_{\R'}$, is a pair of mappings $(\Pi_s, \Pi_o)$, where $\Pi_s$ maps quantum states in $\R$ onto quantum states in $\R'$, and $\Pi_o$ maps free operations in $\R$ onto free operations in $\R'$. 
Moreover, these obey
	\begin{enumerate}
        \item $\rho_1 \prec_\R \rho_2$ whenever $\Pis(\rho_1) \prec_{\R'} \Pis(\rho_2)$;
        \item $\E = \E_1 \circ \E_2$ whenever $\Pio(\E) = \Pio(\E_1) \circ \Pio(\E_2)$.
    \end{enumerate}
We call $\R'$ a \emph{contravariant fragment} of $\R$.
\end{definition}
The use of covariant and contravariant in~\cref{def:covproj,def:contraproj} refers to the direction of implication between the two pre-orders and operation compositions\footnote{Note that strictly these are not projections in the sense of $\Pi^2 = \Pi$, but are instead morphisms. 
Here our use of the term projection is motivated by the idea that one one generally loses information about $\R$ under the mapping.}.

\nick{Perhaps scrap definition of contravariant projection and define contravariant fragment as a subtheory $\R'$ where there exists a (injective) covariant projection from $\R'$ to parent theory $\R$. That would make every subtheory $\R' = (\F', \O')$ a contravariant fragment if $\O'$ is closed under composition, this includes $\sigma$--fragments.}
